---
title: "Analysis title"
subtitle: "A concise description of the report"
author:
  - name: "Your name"
    affiliation: "Your school, faculty or organisation"
date: today
date-format: "D MMMM YYYY"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    theme: cosmo
    css: styles.css
    code-fold: true
    code-summary: "Show the R code"
    code-copy: true
    code-overflow: wrap
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

## Research question

State the question before presenting the analysis. Name the population, variables and comparison as precisely as the available data allow.

## Setup

The setup cell loads packages and defines document-wide objects. `include: false` runs the cell without placing its code, messages or output in the report.

```{r}
#| label: setup
#| include: false

set.seed(42)
```

## Data

Describe where the data came from, what one row represents and any important exclusions or transformations.

```{r}
#| label: inspect-data

analysis_data <- mtcars
head(analysis_data)
```

## Results

Report the estimate and its uncertainty, then explain what they mean in the context of the question.

```{r}
#| label: fig-outcome-distribution
#| fig-cap: "Distribution of miles per gallon in the example data."
#| fig-alt: "A histogram of miles per gallon values, with most observations between 15 and 25."
#| fig-width: 7
#| fig-height: 4

hist(
  analysis_data$mpg,
  col = "#214c57",
  border = "white",
  main = NULL,
  xlab = "Miles per gallon"
)
```

Figure @fig-outcome-distribution shows the outcome distribution before modelling.

::: {.callout-note}
## Interpretation

Replace this note with the main conclusion, expressed in ordinary language and with appropriate limits.
:::

## Reproducibility

```{r}
#| label: session-information
#| echo: false

sessionInfo()
```
